### 2014-03-13 LaTeX/RhodiumConcl.tex
mods to outline

\begin{itemize}
	\item Note that sub-state conflict location may have implications for contagion.  Are regional economic consequences of civil war not a function of civil war existence but proximity of the conflict to cities or resources in neighboring states?
\end{itemize}

>>>>

Contributed to our understanding of why some civil conflicts impact economic performance more severely than others using a novel spatial approach.

Note that sub-state conflict location may have implications for contagion.  Are regional economic consequences of civil war not a function of civil war existence but proximity of the conflict to cities or resources in neighboring states?

### 2014-03-13 LaTeX/RhodiumEmp.tex
mods to outline

\begin{itemize}
	\item Note data aggregation choices.  Multiple conflicts in one country?
	\item Note dropping interstate conflict.
	\item Describe city data collection.
\end{itemize}

>>>>

\subsection{Data and Sample}

Conflict data: comes from PRIO Conflict Location Even Data

	Note data aggregation choices.  Multiple conflicts in one country?

	Note dropping interstate conflict.

City data: Collection of major population centers by year

World Bank data: Econ indicators

Variables: Determined distance between conflicts in a year and city centers. then calculcate min distance to determine effect on conflict

\subsection{Sample and Estimation Method}

Sample: Only country-years undergoing a civil conflict. Coverage restricted to 1989-2008.

Measured as a random effects model with country effects

\subsection{Results}

Maybe we should begin this section by showing the distribution of econ performance among the cntry-years in the dataset. this would illustrate that there is noticeable variation in economic performance to explain.

Conflicts occuring more proximate to major cities have stronger adverse effects on economic performance than those farther away.

### 2014-03-13 LaTeX/RhodiumIntro.tex
mods to outline

Mexico case: high levels of violence since 2008 but little effect on economic growth

Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet. When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?

@@

>>>>

Puzzle: Why do some conflicts have immediate impacts on a country's economy while others that fester for decades have little to no impact.

	Mexico case: high levels of violence since 2008 but little effect on economic growth. Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet. When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?

@@

Background: Show charts of Mexico and/or India's growth in GDP per capita versus number/duration of conflicts

Spatial Dist Hypothesis: Location of conflicts to major cities and capitals determine effect of civil conflict on economic performance

### 2014-03-13 LaTeX/RhodiumLit.tex
Model updates, slight outline updates
mods to outline

\begin{itemize}
	\item varying hypotheses about the effect of war on economic development, war ruin v war renewal hypotheses
	\item 
\end{itemize}

>>>>

varying hypotheses about the effect of war on economic development, war ruin v war renewal hypotheses

literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)

literature on sub-state determinants of conflict and outcome (pierskala hollenbach 2013)

literature on application of spatial variables to studying conflict and how it hasnt captures what we are doing at the sub-national level with city data
